Measurement and Probability in Fuzzy Quantum Theories

### 2016-12-06 prop.tex
prop.tex \section{Conclusion and Discussion} Updating...

If we insist that probabilities cannot be computed to infinite precision
and are bound to be approximations represented by intervals of confidence,
then quantum states themselves can only be discussed within intervals
of confidence. This raises an important philosophical question with
immense practical relevance in the context of quantum computing. The
question, which we could largely bypass in the classical case, is
whether there is, in the background of all the measurements and probabilities,
a ``real'' infinitely-precise quantum state that is being approximated
and that, in principle, can be more and more accurately described
given more and more resources. Although a coarse quantum interval-valued
probability measure may not be induced by one infinitely-precise quantum
state, it might be induced by many quantum states when we examine
different part of its probability assignment. Our examples and Gleason's
theorem suggests that when we increase the measurement resources,
interval-valued probability measures could more and more likely be
identified to a particular state as shown in table~\ref{table_long}.
\begin{table}[ht]
\center{%
\begin{tabular}{c|cccc}
Measurement resources & Lowest & \multicolumn{2}{c}{$\longleftrightarrow$} & Highest\tabularnewline
\hline 
Count of $\mathscr{I}$ & $3$ & $4$ & \ldots{} & $\infty$\tabularnewline
$\sup_{\left[l,r\right]\in\mathscr{I}}\left|r-l\right|$ & $1$ & $\frac{1}{2}$ & \ldots{} & $0$\tabularnewline
Count of $\mathrm{core}\left(\bar{\mu}\right)$ & 0 & 0 &  & 1\tabularnewline
Count of states might correspond to $\bar{\mu}$ & $3$ & $2$ & \ldots{} & $1$\tabularnewline
\hline 
How precise we could identify a state? & Coarse & \multicolumn{2}{c}{$\longleftrightarrow$} & Precise\tabularnewline
\end{tabular}}\caption{Relation between measurement resources and interval-valued probability
measures}
\label{table_long}
\end{table}
Additional work is in progress on the following research questions:
\begin{description}
\item [{Research Question.}] Confirm that there is always an interval-valued
probability measure with an empty-core if the length of the interval
is bigger than zero. 
\item [{Research Question.}] In example~\ref{ex:three-dimensional-three-value}
and \ref{ex:three-dimensional-4-value}, we pick a possible candidate
corresponding to an interval-valued probability measure by only considering
the state whose interval-valued probability is $\necess$. Find a
general method which could be used to determine whether an interval-valued
probability measure is closer to the Born rule or not. 
\item [{Research Question.}] Confirm that as the number and precision
of the intervals increase the quantum interval-valued probability
measure converges to the measure induced by the Born rule. 
\item [{Research Question.}] Investigate the status of the theorems of
Gleason, Bell~\cite{BellBook1987,Redhead1987-REDINA,peres1995quantum,Jaeger2007}
and Kochen-Specker for quantum interval-valued probability measures.
\end{description}
Although we tried to induce a quantum interval-valued probability
measure from a real quantum state, our investigation leaves an open
question of whether there exists a ``real'' entity that exists independently
of measurements and probabilities. This idea is consistent with the
elegantly recent work on Quantum Bayesianism or QBism~\cite{Fuchs2010,VonBaeyer2016,Fuchs2012},
which suggests that the quantum state is more like an interactive
system in computer science parlance. Moreover, the quantum state is
subjective: each observer has a different view of the quantum system
that is consistent with their previous observations and that allows
that observer, independently of other observers, to assign beliefs
(i.e., probabilities) to possible future interactions.

>>>>

If we insist that probabilities cannot be computed to infinite precision
and are bound to be approximations represented by intervals of confidence,
then quantum states themselves can only be discussed within intervals
of confidence. In contrast with the classical case, we found that
there may be no ``real'' infinitely-precise quantum state that is
being approximated when the approximating interval-value probability
measure is not sufficiently accurate. However, a coarse quantum interval-valued
probability measure might still be induced by many different quantum
states when we examine different part of its probability assignment.
Moreover, our examples and Gleason's theorem suggests that as the
measurement resources increase, interval-valued probability measures
could more and more likely be identified to a particular state as
shown in table~\ref{table_long}. 
\begin{table}[ht]
\center{%
\begin{tabular}{c|cccc}
Measurement resources & Lowest & \multicolumn{2}{c}{$\longleftrightarrow$} & Highest\tabularnewline
\hline 
Count of $\mathscr{I}$ & $3$ & $4$ & \ldots{} & $\infty$\tabularnewline
$\sup_{\left[l,r\right]\in\mathscr{I}}\left|r-l\right|$ & $1$ & $\frac{1}{2}$ & \ldots{} & $0$\tabularnewline
Count of $\mathrm{core}\left(\bar{\mu}\right)$ & 0 & 0 &  & 1\tabularnewline
Count of states might correspond to $\bar{\mu}$ & $3$ & $2$ & \ldots{} & $1$\tabularnewline
\hline 
How precise we could identify a state? & Coarse & \multicolumn{2}{c}{$\longleftrightarrow$} & Precise\tabularnewline
\end{tabular}}\caption{Relation between measurement resources and interval-valued probability
measures}
\label{table_long}
\end{table}
Additional work is in progress on the following research questions:
\begin{description}
\item [{Research Question.}] Confirm that there is always an interval-valued
probability measure with an empty-core if the length of the interval
is bigger than zero. 
\item [{Research Question.}] In example~\ref{ex:three-dimensional-three-value}
and \ref{ex:three-dimensional-4-value}, we pick a possible candidate
corresponding to an interval-valued probability measure by only considering
the state whose interval-valued probability is $\necess$. Find a
general method which could be used to determine whether an interval-valued
probability measure is closer to the Born rule or not. 
\item [{Research Question.}] Confirm that as the number and precision
of the intervals increase the quantum interval-valued probability
measure converges to the measure induced by the Born rule. 
\item [{Research Question.}] Investigate the status of the theorems of
Gleason, Bell~\cite{BellBook1987,Redhead1987-REDINA,peres1995quantum,Jaeger2007}
and Kochen-Specker for quantum interval-valued probability measures.
\end{description}
Although we tried to induce a quantum interval-valued probability
measure from a real quantum state, our investigation leaves an open
question of whether there exists a ``real'' entity that exists independently
of measurements and probabilities. This idea is consistent with the
elegantly recent work on Quantum Bayesianism or QBism~\cite{Fuchs2010,VonBaeyer2016,Fuchs2012},
which suggests that the quantum state is more like an interactive
system in computer science parlance. Moreover, the quantum state is
subjective: each observer has a different view of the quantum system
that is consistent with their previous observations and that allows
that observer, independently of other observers, to assign beliefs
(i.e., probabilities) to possible future interactions.
